%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{http://nickhoughton.ca/}{\Large Nick Houghton}} & Email : \href{mailto:nhoughto5@gmail.com}{nhoughto5@gmail.com}\\
		\href{http://nickhoughton.ca/}{www.nickhoughton.ca} & Mobile : +1-310-904-3713 \\
	\end{tabular*}
	\vspace{-10mm}
	\section{}
	\begin{center}
		\Large Software Engineer
		\vspace*{-2mm}
	\end{center}
	Passionate software developer with advanced knowledge of rendering techniques and tools, 3D mathematics, game engines and hardware systems. 
	AI, game-play and systems programmer.
	Multi-language developer.
	Proven use of software design patterns and architecture, development strategies and unit testing.
	Proven research experience. 
	Proven experience with team leadership roles. 
	Skilled in designing, developing, and maintaining software systems with a focus on building efficient and reliable products.
	\textbf{Areas of expertise include:}
	\begin{multicols}{4}
		\begin{itemize}
			\setlength\itemsep{-2mm}
			\item Unity 5
			\item Unreal Engine 4
			\item Blender
			\item C++
			\item GLSL
			\item JavaScript
			\item C\#
			\item 3D Mathematics 
			\item Algorithms 
			\item OpenGL \& WebGL
			\item Git
			\item Java
		\end{itemize}
	\end{multicols}
	%-----------PROJECTS-----------------
	\section{Projects}
	\resumeSubHeadingListStart
	\resumeSubItem{Dead Earth: A first person shooter using Unity 5 and C\#}{}
	\begin{multicols}{2}
		\begin{itemize}
			\setlength\itemsep{0em}
			\item Implemented AI enemies
			\item Achieved blood effects with HLSL shaders
		\end{itemize}	
	\end{multicols}
	\vspace*{-5mm}
	\resumeSubItem{Jump-Ship: A 2D space shooter using Unity 5 and C\#}{}
	\begin{multicols}{2}
		\begin{itemize}
			\setlength\itemsep{0em}
			\item Created weapon mechanics
			\item Implemented AI enemies
		\end{itemize}
	\end{multicols}
	\vspace*{-5mm}
	\resumeSubItem{Unreal Development Online Course}{}
	\begin{multicols}{2}
		\begin{itemize}
			\setlength\itemsep{0em}
			\item Completed two 3D games with \textbf{UE4}: Building Escape, Battle Tank
			\item Improved on combat mechanics
			\item Implemented AI tank enemies
			\item Designed a main menu
			\item Designed battle landscapes
			
		\end{itemize}
	\end{multicols}
	\vspace*{-5mm}
	\resumeSubItem{Zombie-Hunt: A first person shooter made with OpenGL and C++}{}
	\begin{multicols}{2}
		\begin{itemize}
			\setlength\itemsep{0em}
			\item Implemented AI enemies
			\item Created weapon animations in \textit{Blender}
			\item Created a custom renderer
			\item Created a custom .OBJ file importer
		\end{itemize}
	\end{multicols}
	\resumeSubHeadingListEnd
	
	
	%-----------EXPERIENCE-----------------
	\vspace*{-6mm}
	\section{Experience}
	\resumeSubHeadingListStart
	
	%%% JibJab %%%
	\resumeSubheading
	{JibJab Studios}{Marina Del Rey, California}
	{Software Engineer}{May 2017 - Present}
	\begin{itemize}
		\setlength\itemsep{0em}
		\item Developed and maintained a render library in both OpenGL and WebGL
		\item Spearheaded development and operation of a mass gif rendering system using java and Amazon Web Services (AWS)
		\item Installed render library with EmberJS, React and iOS applications
		\item Implemented shell scripts to automate render tasks using FFMPEG
	\end{itemize}
	
	%%% ONC %%%
	\resumeSubheading
	{Ocean Networks Canada}{Victoria B.C.}
	{Software Engineer}{May 2016 - Apr 2017}
	\begin{itemize}
		\setlength\itemsep{0em}
		\item Developed large scale oceanic data API with JavaEE
		\item Improved server performance using JMeter load testing
		\item Designed and developed user-facing features using Javascript, HTML5 and CSS3.
	\end{itemize}
	
	%%% ONC %%%
	\resumeSubheading
	{University of Victoria}{Victoria B.C.}
	{Hardware Security Fellow}{May 2015 - Dec 2016}
	\begin{itemize}
		\setlength\itemsep{0em}
		\item Developed a hardware trojan detection application using Java
		\item Designed and implemented a protoype of a new homomorphic encryption algorithm using C++.
	\end{itemize}
	\resumeSubHeadingListEnd
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{University of Victoria}{Victoria B.C. Canada}
	{Masters of Applied Science in Computer Engineering}{May. 2015 -- Dec. 2016}
	\resumeSubheading
	{University of Victoria}{Victoria B.C. Canada}
	{Bachelor of Engineering in Computer Engineering}{Sept. 2010 -- Apr. 2015}
	\resumeSubHeadingListEnd
	%-------------------------------------------
\end{document}