%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Nick}{Houghton}
\title{Resumé}                               % optional, remove / comment the line if not wanted
\address{2446 Sinclair Rd}{Victoria B.C.}{Canada}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(250)~893~1988}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{nhoughto5@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.nickhoughton.ca}                         % optional, remove / comment the line if not wanted
\extrainfo{www.linkedin.com/in/nghoughton}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Profile}
Software engineer with 3+ years experience. 
Proficient with industrial software development and cutting edge research.
Proven experience working in collaborative environments, leadership roles and self-reliant projects.
Skilled in designing, developing, and maintaining software systems with a focus on building efficient and reliable products.
\section{Key Competencies}
\begin{itemize}
	\item Comprehensive knowledge and skills with the latest generation of both the C++ and Java programming languages. Additionally experienced with C\#, Javascript, SQL, HTML, CSS, and more.
	\item Game development experience with Unreal Engine 4 and Unity 5.
	\item Game development and physical simulation experience with the C++ APIs OpenGL and DirectX.
	\item Experience developing and maintaining large scale distributed system using Java.
	\item Experienced with Agile methodologies.
	\item Experience with version control using both \textit{Subversion} and \textit{Git}.
	\item Considerable experience with customer relations in industrial settings.
	\item Multiple academic publications.
	\item Passion for continued learning and skill development.
	\item Positive attitude.
	\item Extensive first-aid training.
\end{itemize}

\section{Experience}
%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{2016--2017}{Software Engineer/Developer}{Ocean Networks Canada}{Victoria B.C.}{}{Developed and maintained the data management and acquisition service (DMAS). This service ingests over 200 Terabytes of information a day while performing quality assurance analysis, data product generation, management of the large device network and hosting a web-based user interface.\newline{}%
\begin{itemize}%
\item Developed \textit{RESTful} web services using Java and Hibernate.
\item Designed and developed user-interface applications with Javascript, HTML and CSS.
\item Adapted database designs for continually changing models. Used SQL with \textit{Oracle} and CQL with \textit{Cassandra.}
\item Performance testing using \textit{JMeter}.
\item Employed version control with \textit{Subversion}.
\item Employed agile methodologies using the \textit{Jira} ticketing system.
\end{itemize}}
\clearpage
%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{2015--2016}{Hardware Security Fellow}{University of Victoria}{Victoria B.C.}{}{Member of the Uvic hardware security fellowship. Studied the existence, characteristics, and impact of maliciously modified integrated circuits. Developed applications, tools, and techniques to combat industrial or military sabotage of computer hardware.
	\newline{}
\begin{itemize}
	\item Developed an application which can automatically detect and analyze hardware trojans in Field-programmable gate-arrays using Java and the \textit{RapidSmith} library.
	\item Assisted in the development of a comprehensive topology to describe and organize characteristics of hardware trojans.
	\item Developed a web-based series of trojan analysis tools using ASP.NET and C\#. 
	\item Published four academic papers.
\end{itemize}}

%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{2015--2015}{Teaching Assistant}{University of Victoria}{Victoria B.C.}{}{Instructed and managed a laboratory section of Uvic Engineering's Computer Engineering 255: Computer Architecture class. The laboratories focused on exposing students to assembly programming, embedded system architecture and algorithm design.\newline{}
\begin{itemize}
	\item Became intimately familiar with embedded C programming, the \textit{ARM} assembler language, low-level algorithm design and implementation, and platform architecture.
	\item Debug student code and troubleshot classroom equipment.
	\item Gave instructional lectures.
	\item Marked assignments.
	\item Recorded student grades.
\end{itemize}}

%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{2014--2015}{Research Assistant}{University of Victoria}{Victoria B.C.}{}{Selected to be a member of the cryptographic research fellowship under the supervision of Dr. Fayez Gebali. Responsible for the proof-of-concept C++ implementation of an experimental homomorphic encryption algorithm.\newline{}
\begin{itemize}
	\item Became intimately familiar with the practices of encryption, homomorphic algorithms and discrete mathematics.
	\item Designed and developed a proof-of-concept implementation of experimental algorithm using C++.
	\item Employed the \textit{WestGrid} super-computer network to execute large, resource demanding experiments.
	\item Designed and developed a simple client-server system which encrypted/decrypted messages, performed performance analysis, and managed message transmission.
	\item Co-wrote and published an academic paper on findings.
\end{itemize}}

%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{2011--2011}{Co-op Employee}{MMM Group}{Vancouver B.C.}{}{Assisted Senior Project Engineers and Project Managers design and execute designs of power distribution, lighting and emergency systems in large-scale construction projects.\newline{}
\begin{itemize}
	\item Drafted and reviewed project plans using \textit{AutoCad}.
	\item Designed and developed an award calculator for LEED's mercury-content, 'green'-design award using Excel and Visual Basic.
	\item Communicated with clients and suppliers on project progress and needs.
	\item Performed project site inspections.
\end{itemize}}

%%%%%% Employer %%%%%%%%%%%%%%%
%\cventry{2006--2015}{Aquatic Team Leader / Lifeguard}{Saanich Commonwealth Place}{Victoria B.C.}{}{Employed as a lifeguard during high-school and undergraduate studies; promoted to Aquatic Team Leader.\newline{}
%\begin{itemize}
%	\item Responsible for supervision and management of aquatic staff.
%	\item Performed incident management, first-aid quality assessment and emergency services interaction.
%	\item Partook in first aid and lifeguarding technique training and instruction.
%\end{itemize}}

\clearpage
% ================== Education ===============%
\section{Education}
\cventry{2015--2016}{Masters of Applied Science}{University of Victoria}{Victoria}{\textit{3.0 GPA}}{
	\begin{itemize}
		\item Wrote and published a thesis.
		\item Invented an application which automatically detects hardware trojan viruses in field-programmable gate-arrays. Written in Java.
		\item Three published academic papers. One pending.
		\item Gained experience as a teaching assistant for an embedded systems programming class.
		\item Gave a presentation on hardware trojans at the \textit{International Workshop on Information Security, Assurance, and Trust} (I-SAT 2016).
	\end{itemize}
}
\cventry{2011--2015}{Bachelor of Engineering}{University of Victoria}{Victoria}{\textit{Computer Engineering}}{
	\begin{itemize}
		\item Graduated with both the \textit{Networks, Security and Privacy} and the \textit{Digital and Embedded Systems} specialties.
		\item Won third place in the IEEE Student Technical Design Competition.
	\end{itemize}
}  % arguments 3 to 6 can be left empty

\subsection{Continuing Education and Personal Projects}
\footnotesize
*Visit my website for more details, demonstrations and walkthroughs.\newline\newline
\normalsize
% ========= Personal Project =========== %
\cventry{2016}{Unreal Engine Developer Course}{Udemy.com}{Online}{}{
\begin{itemize}
	\item Completed three 3D games: Building Escape, Battle Tank, and Testing Grounds.
	\item Became intimately familiar Unreal Engine 4 developer interface.
	\item Studied material development and design.
	\item Familiar with both C++ and Blueprint development methodologies.
\end{itemize}
}
% ========= Personal Project =========== %
\cventry{2016}{Unity 5: Jump-Ship}{Personal Project}{}{}{
\begin{itemize}
	\item Created a 2D space shooter game. 
	\item Created sprites.
	\item Developed game mechanics and enemy AI in C\#.
	\item Developed user-interface using the canvas system.
	\item Created simple explosion animations.
\end{itemize}
}

% ========= Personal Project =========== %
\cventry{2015--2016}{OpenGL: Various Projects using C++}{Personal Projects}{}{}{
\begin{itemize}
	\item Created a first person shooter called 'Zombie-Hunt'.
	\item Created a simulation of globular physics spurting from a fountain which employed an implicit mesher.
	\item Created a 2D simulation of a pendulum-cart system using Lagrangian Mechanics.
\end{itemize}
}

%\section{Master's Thesis}
%\cvitem{Title}{\emph{Automated Trojan Detection and Analysis in Field Programmable Gate Arrays}}
%\cvitem{Supervisors}{Dr. Fayez Gebali, Dr. Samer Moein}
%\cvitem{Description}{
%	Electronics have become such a staple in modern life that we are just as affected by their vulnerabilities as they are.
%	Ensuring that the processors that control them are secure is paramount to our intellectual safety, our financial safety, our privacy, and even our personal safety.
%	The market for integrated circuits is steadily being consumed by a reconfigurable type of processor known as a field-programmable gate-array (FPGA).
%	The very features that make this type of device so successful also make them susceptible to attack.
%	FPGAs are reconfigured by software; this makes it easy for attackers to make modification.
%	Such modifications are known as hardware trojans.
%	There have been many techniques and strategies to ensure that these devices are free from trojans but few have taken advantage of the central feature of these devices.
%	The configuration Bitstream is the binary file which programs these devices.
%	By extracting and analyzing it, a much more accurate and efficient means of detecting trojans can be achieved.
%	This discussion presents a new methodology for exploiting the power of the configuration Bitstream to detect and described hardware trojans.
%	A software application is developed that automates this methodology.	
%}

%\section{Languages}
%\cvitemwithcomment{Language 1}{Skill level}{Comment}
%\cvitemwithcomment{Language 2}{Skill level}{Comment}
%\cvitemwithcomment{Language 3}{Skill level}{Comment}
%
%\section{Computer skills}
%\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}
%
%\section{Interests}
%\cvitem{hobby 1}{Description}
%\cvitem{hobby 2}{Description}
%\cvitem{hobby 3}{Description}
%
%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}
%
%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}

%	\item{Dr. Brian Wyvill}{Computer Science
%		University of Victoria
%		Email: bwyvill@uvic.ca
%		Phone:250 472 5760}
%	\item{Dr. Fayez Gebali}{Electrical and Computer Engineering
%		University of Victoria
%		Email: Fayez@ece.uvic.ca
%		Phone: 250 721 6036}

\section{References}
\begin{cvcolumns}
\cvcolumn{Dr. Brian Wyvill}{
	\begin{itemize}
		\item Prof.~of Computer Science.
		\item University of Victoria
		\item Email:~bwyvill@uvic.ca
		\item Phone:~250~472-5760
	\end{itemize}}
\cvcolumn{Dr. Fayez Gebali}{
	\begin{itemize}
		\item Prof.~of Electrical and Computer Engineering.
		\item University of Victoria
		\item Email:~Fayez@ece.uvic.ca
		\item Phone:~250~721-6509 
	\end{itemize}}
\cvcolumn{Dr. Samer Moein}{
  	\begin{itemize}
  		\item Prof.~of Electrical and Computer Engineering.
  		\item University of Victoria
		\item Email:~samerm@uvic.ca
		\item Phone:~250~721-6509 
  	\end{itemize}}
\end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%\clearpage
%%-----       letter       ---------------------------------------------------------
%% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle
%
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.
%
%Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.
%
%Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.
%
%Albert Einstein discovered that $e=mc^2$ in 1905.
%
%\[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]
%
%\makeletterclosing
%
%%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
